HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
%\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

Human judgement is the central, and perhaps most fundamental, criterion for
estimating the quality of an MT system.
Nevertheless, common measures for MT evaluation, such as adequacy and fluency judgements
or the relative ranking of several possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number that quantifies the quality of the entire sentence. This
is indeed reflected in the diminishing inter-annotator agreement rates of human ranking measures
as a function of the sentence length \cite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are erroneously translated, and hence cannot inform developers in overcoming these errors.

These problems were partially addressed by measures that decompose over sub-parts of the evaluated
translation sentence (henceforth, {\it translation}),
most commonly over its words or n-grams,
quantifying the overlap of its sub-parts relative a reference translation.
More recent work on MT evaluation proposed measures
that decompose over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
These measures can localize semantic errors in the translation, but
their focus on verb argument structures misses many pervasive semantic phenomena
(such as inter-clause linkage and nominal argument structures) and thus they only provide
a limited perspective on the semantic similarity between the output and reference.
Moreover, assigning semantic structure to MT output, especially when low in quality,
is difficult and arguably ill-defined.

@@

\def\iaafig #1{\includegraphics[width=3.8cm]{iaa_length_#1.png}}

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure}

@@

\def\iaafig #1{\includegraphics[width=3.8cm]{iaa_heatmap_#1.png}}

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

}
\end{tabular}
\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
\label{fig:heatmap}
\end{figure}

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

Human judgement is the central, and perhaps most fundamental, criterion for
estimating the quality of an MT system.
Nevertheless, common measures for MT evaluation, such as adequacy and fluency judgements
or the relative ranking of several possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number that quantifies the quality of the entire sentence. This
is indeed reflected in the diminishing inter-annotator agreement (IAA) rates of human ranking measures
%as a function of
with
the sentence length \cite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are erroneously translated, and hence cannot inform developers in overcoming these errors.

These problems are partially addressed by measures that decompose over sub-parts of the evaluated
translation sentence (henceforth, {\it translation}). For automatic measures,
these are commonly words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
\XXX{Do we want to cut the following shorter?}
These measures can localize semantic errors in the translation, but
their focus on verb argument structures misses many pervasive semantic phenomena
(such as inter-clause linkage and nominal argument structures) and thus they only provide
a limited perspective on the semantic similarity between the output and reference.
Moreover, assigning semantic structure to MT output, especially when low in quality,
is difficult and arguably ill-defined.

@@

\def\iaafig #1{\includegraphics[width=7cm]{iaa_length_#1.png}}

\begin{figure*}[ht!]
\begin{tabular}{cc}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure*}

\def\iaafig #1{\includegraphics[width=7cm]{iaa_heatmap_#1.png}}

%\begin{figure*}[ht!]
%\begin{tabular}{cc}
%
%
%\subfloat[English-Czech]{
%  \iaafig{cs}
%}
%&
%\subfloat[English-German]{
%  \iaafig{de}
%
%}
%\\
%
%\subfloat[English-Polish]{
%  \iaafig{pl}
%  
%}
%&
%\subfloat[English-Romanian]{
%  \iaafig{ro}
%
%}
%\end{tabular}
%\caption{Confusion matrices for each of the language pairs, plotted as heatmaps.}
%\label{fig:heatmap}
%\end{figure*}

@@
